Political Polarization, Public Trust, and Healthcare Disparities: Unraveling COVID-19's Impact and Future Preparedness

### 2024-02-14 outputs/paper/paper.qmd
updated a few peer reviews

---
title: "Political Polarization, Public Trust, and Healthcare Disparities: Unraveling COVID-19's Impact and Future Preparedness"
author: 
  - Adrian Ly
  - Hannah Yu
  - Sakhil Goel
thanks: "Code and data are available at: https://github.com/hannahyu07/US-Covid-Analysis.git"
date: today
date-format: long
abstract: "The COVID-19 pandemic has exposed deep disparities in health outcomes across different states and counties in the United States. We use data from the American Economic Association to conduct a comprehensive analysis of how variances in local health infrastructure and socio-political factors within the United States contributed to disparities in COVID-19 outcomes. Our analysis reveals that political polarization significantly influenced adherence to health guidelines, with Republican-leaning states demonstrating slightly higher clustering around elevated death rates. Moreover, social vulnerabilities, including disparities in healthcare access, housing conditions, and ethnic demographics, emerged as key contributors to substantial variations in disease outcomes. These results highlight the urgent requirement for customized public health readiness and response tactics, focusing on precise interventions to tackle deficiencies in community health infrastructure and socio-political factors."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

*This reproduction was performed after a replication on the Social Science Reproduction platform: ****[link here](https://www.socialsciencereproduction.org/reproductions/c35e8e98-762d-4c00-a1a3-544ed0b2008d/index)***

@@

The datasets utilized in this paper were mainly obtained from the `original paper` [@citearticle]. The data used by the paper was compiled from various sources such as the @data1, @data2, @data3, @data4, @data5, @data6, @data7, @data8, @data9, @data10, and @data11. Additionally, to address the original paper's lack of US COVID statistics and political party support data, we incorporated information from @citedata1 and [@citedata2]. The political party support data we utilized from @citedata1 was compiled from @data12.

@@

The transformation of real-world phenomena into quantifiable data points in our dataset is influenced by various factors, leading to inherent limitations in our  measurements for life expectancy rates, and political affiliation.

>>>>

---
title: "Political Polarization, Public Trust, and Healthcare Disparities: Unraveling COVID-19's Impact and Future Preparedness"
author: 
  - Adrian Ly
  - Hannah Yu
  - Sakhil Goel
thanks: "Code and data are available at: https://github.com/hannahyu07/US-Covid-Analysis.git 
This reproduction was performed after a replication on the Social Science Reproduction platform: [link here](https://www.socialsciencereproduction.org/reproductions/c35e8e98-762d-4c00-a1a3-544ed0b2008d/index)"
date: today
date-format: long
abstract: "The COVID-19 pandemic has exposed deep disparities in health outcomes across different states and counties in the United States. We use data from the American Economic Association to conduct a comprehensive analysis of how variances in local health infrastructure and socio-political factors within the United States contributed to disparities in COVID-19 outcomes. Our analysis reveals that political polarization significantly influenced adherence to health guidelines, with Republican-leaning states demonstrating slightly higher clustering around elevated death rates. Moreover, social vulnerabilities, including disparities in healthcare access, housing conditions, and ethnic demographics, emerged as key contributors to substantial variations in disease outcomes. These results highlight the urgent requirement for customized public health readiness and response tactics, focusing on precise interventions to tackle deficiencies in community health infrastructure and socio-political factors."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

@@

The datasets utilized in the `original paper` [@citearticle] and this paper were mainly compiled from various sources such as the @data1, @data2, @data3, @data4, @data5, @data6, @data7, @data8, @data9, @data10, and @data11. Additionally, to address the original paper's lack of US COVID statistics and political party support data, we incorporated information from @citedata1 and [@citedata2]. The political party support data we utilized from @citedata1 was compiled from @data12.

@@

The transformation of real-world phenomena into quantifiable data points in our dataset is influenced by various factors, leading to inherent limitations in our  measurements for life expectancy rates [@citedefenition], and political affiliation.
